Compare NE-combined vs. NE-separated reference

### 2025-07-09 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/separate-tumor.Rmd
Apply suggestions from code review
Co-authored-by: Ally Hawkins <54039191+allyhawkins@users.noreply.github.com>

Below we print the intersection of these two sets of marker genes for each cell type comparison:
```{r}
separated_cell_types <- names(ne_markers)
non_neuro_cell_types <- separated_cell_types[!(stringr::str_detect(separated_cell_types, "Neuro"))]

@@

That said, note that there are likely very different numbers of cells labeled as `NE` and `NE-tumor`, which may influence how these plots are interpreted.
```{r}
celltype_df |>
  dplyr::filter(stringr::str_detect(singler_label_separated, "Neuro")) |>
  dplyr::count(singler_label_separated)
```

```{r}
combined_marker_genes <- model_combined$markers$full$Neuroendocrine |>
  purrr::reduce(c) |>
  unique()

cell_types <- names(ne_markers)
non_neuro_cell_types <- cell_types[!(stringr::str_detect(cell_types, "Neuro"))]

@@

```{r}
celltype_df |>
  dplyr::filter(
    singler_label_combined == "Neuroendocrine" | stringr::str_detect(singler_label_separated, "Neuroendocrine")
  ) |>
  dplyr::count(singler_label_combined, singler_label_separated) |>
  dplyr::arrange(desc(n))
```

### Cells with different labels between models

Next, we'll print a table that directly shows the counts of cells with different labels as inferred with either model.

```{r}
celltype_df |>
  dplyr::filter(singler_label_combined != singler_label_separated) |>
  dplyr::count(singler_label_combined, singler_label_separated) |>
  dplyr::arrange(desc(n))
```

>>>>

Below we print the intersection of these two sets of marker genes for each cell type comparison:
```{r}
separated_cell_types <- names(ne_markers)
non_neuro_cell_types <- separated_cell_types[!(stringr::str_detect(separated_cell_types, "Neuroendocrine"))]

@@

That said, note that there are likely very different numbers of cells labeled as `NE` and `NE-tumor`, which may influence how these plots are interpreted.
```{r}
celltype_df |>
  dplyr::filter(stringr::str_detect(singler_label_separated, "Neuroendocrine")) |>
  dplyr::count(singler_label_separated)
```

```{r}
ne_marker_genes <- model_separated$markers$full$Neuroendocrine |>
  purrr::reduce(c) |>
  unique()

 ne.tumor_marker_genes <- model_separated$markers$full$`Neuroendocrine-tumor` |>
  purrr::reduce(c) |>
  unique()

ne_only <- setdiff(ne_marker_genes, ne.tumor_marker_genes)
ne.tumor_only <- setdiff(ne.tumor_marker_genes, ne_marker_genes) 
cell_types <- names(ne_markers)
non_neuro_cell_types <- cell_types[!(stringr::str_detect(cell_types, "Neuro"))]

@@

```{r}
celltype_df |>
  dplyr::count(singler_label_combined, singler_label_separated) |>
  dplyr::arrange(desc(n))
```
